---
title: "2016-2021 Men's Ice Hockey Revenue Report"
author: "Zachary Lazerick"
date: '2022-08-04'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

**Introduction**
 
In this document, there  will be a discussion of the performance of the Men's Ice Hockey Season Ticket Program from the 2016 season until the 2021 season. This will be done utilizing metrics like Account Holders, Tickets Sold, Revenue Earned, etc. Using this data, it will be determined whether the Men's Ice Hockey Season Ticket Program is growing, shrinking, or neither. 

**The Data**

Below is a brief summary of all data collected:

Season -- Men's Hockey Season, ex. 2021 == 2021-22 Season

Renewed Accounts -- The number of Season Ticket Holders that accepted their renewal offers. This is defined as any Season Ticket Holders that had purchased at least what they had purchased the previous season. 

Renewed Tickets -- The number of Season TicketS purchased from Renewed Accounts.

Renewed Revenue -- The amount of Revenue earned from Renewed Season Ticket purchases. This is measured in USD ($). 

New Accounts -- The number of Season Ticket Holders that bought Season Tickets, but did not have a renewal offer. 

New Tickets -- The number fo Season Tickets purchased from New Accounts. 

New Revenue -- The amount of Revenue earned from New Season Ticket purchases. This is measured in USD ($).

Renewal Rate -- The proportion of Season Ticket Offers that were Renewed from the previous season. This is measured as a percentage (%).

Total Accounts -- The Total number of Season Ticket Holders, calculated as Renewed + New Accounts.

Total Tickets -- The Total number of Season Tickets purchased, calculated as Renewed + New Tickets.

Total Revenue -- The Total amount of Revenue earned from Season Ticket purchases, calculated as Renewed + New Revenue. 

```{r, include = F}
##Read in Data
MIHRR <- read.csv("2016_2021MIHRR.csv")

attach(MIHRR)
```

**Acknowledgements and Assumptions**

1) All data is obtained from end-of-season Revenue Reports. Accuracy of conclusions made in this report are predicated on the accuracy of the information provide in said Revenue Reports. 

2) Due to the COVID-19 pandemic, fan attendance was not permitted for the 2020-21 Men's Hockey Season, and as such, season tickets were not available to purchase. Therefore, the 2020-21 Season should be regarded as a "hole", as in no data, in any graph it "appears". 

\pagebreak

**Part I: Metric Totals**

As mentioned previously, this document will utilize sales metrics to assess the performance of the Men's Ice Hockey Season Ticket program. To start, a look at end-of-Season Totals for the number of Season Ticket Accounts, Season Tickets Sold, and Season Ticket Revenue. 

Below are plots for each of these metrics:

```{r, out.width = "50%", out.height = "50%"}
##Total Accounts
plot(Season, TotalAccounts, type = "l", col = "red", lwd = 3, 
     main = "Total Season Ticket Accounts per Season", 
     xlab = "Season", ylab = "Accounts")

##Total Tickets
plot(Season, TotalTickets, type = "l", col = "red", lwd = 3, 
     main = "Total Season Tickets Sold per Season", 
     xlab = "Season", ylab = "Tickets")
```

```{r, fig.align = "center", out.width = "50%", out.height = "50%"}
##Total Revenue
plot(Season, TotalRevenue, type = "l", col = "red", lwd = 3, 
     main = "Total Season Ticket Revenue Earned per Season", 
     xlab = "Season", ylab = "Revenue ($)")
```

Here we see that after recovering from a decline in Total Season Ticket Metrics in 2018, the Men's Ice Hockey Season Ticket Program appears to be growing, or rather returning to previous highs from the 2016 Season. Without more data, both past and future, proof of the true nature of this growth is indecipherable at this time. 

\pagebreak

With that context, the breakdown of these metrics into Renewed vs. New Metrics is as follows:

```{r, out.width = "50%", out.height = "50%"}
##Barplot Renewed vs. New Accounts
cols <- c("red", "blue")
par(lwd = 1)
barplot(t(MIHRR[c("RenewedAccounts", "NewAccounts")]), 
        beside = T, 
        ylim = c(0, max(MIHRR[c("RenewedAccounts", "NewAccounts")]) * 1.5), 
        border = cols, col = cols, names.arg = MIHRR$Season, 
        main = "Renewed vs. New Accounts", 
        xlab = "Season", ylab = "Accounts")
box()
legend("topright", cex = 1, fill = cols, 
       legend = c("Renewed Accounts", "New Accounts"))

##Barplot Renewed vs. New Tickets
cols <- c("red", "blue")
par(lwd = 1)
barplot(t(MIHRR[c("RenewedTickets", "NewTickets")]), 
        beside = T, 
        ylim = c(0, max(MIHRR[c("RenewedTickets", "NewTickets")]) * 1.5), 
        border = cols, col = cols, names.arg = MIHRR$Season, 
        main = "Renewed vs. New Tickets", 
        xlab = "Season", ylab = "Tickets")
box()
legend("topright", cex = 1, fill = cols, 
       legend = c("Renewed Tickets", "New Tickets"))
```

```{r, fig.align = "center", out.width = "50%", out.height = "50%"}
##Barplot Renewed vs. New Revenue
cols <- c("red", "blue")
par(lwd = 1)
barplot(t(MIHRR[c("RenewedRevenue", "NewRevenue")]), 
        beside = T, 
        ylim = c(0, max(MIHRR[c("RenewedRevenue", "NewRevenue")]) * 1.2), 
        border = cols, col = cols, names.arg = MIHRR$Season, 
        main = "Renewed vs. New Revenue", 
        xlab = "Season", ylab = "Revenue")
box()
legend("topright", cex = 1, fill = cols, 
       legend = c("Renewed Revenue", "New Revenue"))
```

Here we see that the majority of Season Ticket Metrics for the Men's Ice Hockey Season Ticket program can be attributed to New Accounts, New Tickets, and New Revenue. This suggests that fan retention is an issue. The Men's Ice Hockey Season Ticket Program can get people in the door, but can not get them to stick around. 

\pagebreak

**Part II: Renewal Rates**

Now a look at the Renewal Rates for the Men's Ice Hockey Season Ticket Program. But, what is a renewal rate? Traditionally, the renewal rate can be thought of in two separate ways, an Account Renewal Rate, and Ticket Renewal Rate. 

But, how do we calculate this? The Account Renewal Rate for the current season is calculated as follows: Renewed Season Ticket Accounts for Current Season divided by the Total Number of Season Ticket Accounts for the Previous Season, multiplying the result by 100 to obtain the percentage. The Ticket Renewal Rate for the current season would be calculated the exact same way, replacing Accounts for Tickets, of course. As an example, the Account Renewal Rate for the 2019 Season would be calculated as Renewed Season Ticket Accounts in 2019 divided by the Total Number of Season Ticket Accounts in 2018, multiplying the result by 100. 

```{r, include = F}
##Create New Renewal Rate Variables
AccountRenewalRate <- RenewalRate
TicketRenewalRate <- RenewalRate

for (i in 1:4) {
  AccountRenewalRate[i] <- (RenewedAccounts[i] / TotalAccounts[i+1]) * 100
  TicketRenewalRate[i] <- (RenewedTickets[i] / TotalTickets[i+1]) * 100
}

AccountRenewalRate <- round(AccountRenewalRate, digits = 2)
TicketRenewalRate <- round(TicketRenewalRate, digits = 2)
```

With that out of the way, graphs of the Account Renewal Rate and Ticket Renewal Rate are provided below:

```{r, out.width = "50%", out.height = "50%"}
##Account Renewal Rate Plot
plot(Season, AccountRenewalRate, type = "l", col = "red", lwd = 3, 
     main = "Account Renewal Rate per Season", 
     xlab = "Season", ylab = "Rate (%)")

##Ticket Renewal Rate Plot
plot(Season, TicketRenewalRate, type = "l", col = "red", lwd = 3, 
     main = "Ticket Renewal Rate per Season", 
     xlab = "Season", ylab = "Rate (%)")
```

Depending on the reader, one of these metrics may be more important than the other, thinking 'Are more account holders returning to the program, or are more tickets returning to the program?' This can be analyzed by looking at the difference between the Account Renewal Rate, and Ticket Renewal Rate. (For the purposes of this report, Account Renewal Rate minus Ticket Renewal Rate will be analyzed. The results are the same regardless)

```{r, include = F}
##Create Diff. Renewal Rate Variable
DiffRenewalRate <- AccountRenewalRate - TicketRenewalRate
```

A plot of the difference between the Account Renewal Rate and Ticket Renewal Rate is provided below:

```{r, fig.align = "center", out.width = "50%", out.height = "50%"}
plot(Season, DiffRenewalRate, type = "l", col = "red", lwd = 3, 
     main = "Difference in Renewal Rates per Season", 
     xlab = "Season", ylab = "Rate (%)")
```

Here, we see much of the graph shows negative numbers. This means that the Ticket Renewal Rate is greater than the Account Renewal Rate for these seasons. Again, depending on the reader, this can be seen as a positive, because of the overall proportion of Season Tickets Sold is remaining comparatively high compared to overall proportion fo Season Ticket Accounts. 

\pagebreak