---
title: "2022 Football Projections"
author: "Zachary Lazerick"
date: '2022-07-21'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = F}
##Read in Data
STH <- read.csv("FB22STHList_Master.csv")
##Removes 2 Comp Observations From Data Set
STH <- STH[3:nrow(STH), ]
attach(STH)

##Check Grand Totals
Total <- (Tickets * PricePerTicket) + (ParkingPasses * PricePerPass)
isSame <- Total == GrandTotal
count = 0
for (i in 1:nrow(STH)) {
  if (isSame[i] == FALSE) {
    count <- count + 1
  }
}
count

##Create a Payment Hour from Payment Time
PaymentHour <- STH$PaymentTime
##Deletes Last 2 Characters from String
PaymentHour <- substr(PaymentHour, 1, nchar(PaymentHour)-2) 
##Appends "00 on to the End of the String
PaymentHour <- paste(PaymentHour, "00", collapse = NULL)
##Removes the Space in the Middle of the String
PaymentHour <- gsub(" ", '', PaymentHour)

##Set Payment Hour as an Ordered Factor
PaymentHour <- as.factor(PaymentHour)
PaymentHour <- ordered(PaymentHour, levels = c("0:00", "1:00", "2:00", "3:00",
                                               "4:00", "5:00", "6:00", "7:00", 
                                               "8:00", "9:00", "10:00", "11:00",
                                               "12:00", "13:00", "14:00", 
                                               "15:00", "16:00", "17:00", 
                                               "18:00", "19:00", "20:00", 
                                               "21:00", "22:00", "23:00"))

##Set Payment Day of Week as an Ordered Factor
STH$PaymentDoW <- as.factor(STH$PaymentDoW)
STH$PaymentDoW <- ordered(STH$PaymentDoW, levels = c("Sunday", "Monday", "Tuesday", 
                                                     "Wednesday", "Thursday",
                                                     "Friday", "Saturday"))

##Create Order Month Variable
OrderMonth <- PaymentCreateDate
OrderMonth <- substr(OrderMonth, 1, 1)
for (i in 1:nrow(STH)) {
  if (OrderMonth[i] == "4") {
    OrderMonth[i] <- "April"
  }
  else if (OrderMonth[i] == "5") {
    OrderMonth[i] <- "May"
  }
  else if (OrderMonth[i] == "6") {
    OrderMonth[i] <- "June"
  }
  else if (OrderMonth[i] == "7") {
    OrderMonth[i] <- "July"
  }
  else if (OrderMonth[i] == "8") {
    OrderMonth[i] <- "August"
  }
}

##Set OrderMonth as an Ordered Factor
OrderMonth <- as.factor(OrderMonth)
OrderMonth <- ordered(OrderMonth, levels = c("April", "May", "June",
                                             "July", "August"))

##Set Ticket Type as an Ordered Factor
STH$TicketType <- as.factor(STH$TicketType)
STH$TicketType <- ordered(TicketType, levels = c("Reserved Cushion", "Reserved 
                                                 Bleacher", "General Admission",
                                                 "Fitton 4", "None"))

##Set Parking Location as an Ordered Factor
STH$ParkingLocation <- as.factor(STH$ParkingLocation)
STH$ParkingLocation <- ordered(ParkingLocation, levels = c("Baseball Lot", 
                                                           "Freshman Field", 
                                                           "Parking Garage", 
                                                           "West Lot", 
                                                           "Fitton 4", "None"))

##Set Delivery Method as an Ordered Factor
STH$DeliveryMethod <- as.factor(STH$DeliveryMethod)
STH$DeliveryMethod <- ordered(DeliveryMethod, levels = c("Mobile Delivery", 
                                                         "Print at Home", 
                                                         "Mail", 
                                                         "Subscription", 
                                                         "Email"))
```

**Introduction**

In this document, we will look at the 2022 Football Season to analyze the performance of the Season Ticket and Parking Pass Programs for this.

To do this, we will start by looking at total sales thus far, and abstracting this to project total revenue earned through these programs for the start of the 2022 Season. Afterward, we will contextualize these results, comparing their performance to previous seasons.  

Next, we will analyze sale trends data to see where we are over-performing, under-performing, or meeting expectations.

**Assumptions and Acknowledgements**

Accuracy of the conclusions and observations made in this document are predicated on the accuracy of the data obtained from Revenue Snapshots and from reports generated by AudienceView. 

Due to the COVID-19 Pandemic, there was no fan attendance permitted for the 2020 Football Season. Therefore, there were no Season Ticket Sales for this season. Thus, the 2020 Season should be treated as a "hole", as in no data, in any graph that it "appears."

\pagebreak

**Section I: The 2022 Football Season Ticket Holders**

AS mentioned before, in this section, we will calculate total performance metrics for the 2022 Football Season Ticket Program and 2022 Football Parking Program. We will calculate the total number of renewed accounts, renewed tickets, renewed revenue, renewal rate, new accounts, new tickets, new revenue, as well as, total number of parking pass accounts, parking passes, and parking revenue for each parking lot. 

```{r}
##Calculations
##Calculate Season Ticket Account Metrics
RA = 0
RT = 0
RR = 0

SA = 0
ST = 0
SR = 0

RA4 = 0
R4T = 0
R4R = 0

S4A = 0
S4T= 0
S4R= 0

for (i in 1:nrow(STH)) {
  if (OrderType[i] == "R" && BundleName[i] == "FB22") { 
    RA <- RA + 1
    RT <- RT + Tickets[i]
    RR <- RR + (Tickets[i] * PricePerTicket[i])
  }
  else if (OrderType[i] == "S" && BundleName[i] == "FB22") {
    SA <- SA + 1
    ST <- ST + Tickets[i]
    SR <- SR + (Tickets[i] * PricePerTicket[i])
  }
  else if (OrderType[i] == "R" && BundleName[i] == "Fitton 4 Pack") {
    RA4 <- RA4 + 1
    R4T <- R4T + Tickets[i]
    R4R <- R4R + (Tickets[i] * PricePerTicket[i])
  }
  else if (OrderType[i] == "S" && BundleName[i] == "Fitton 4 Pack") {
    S4A <- S4A + 1
    S4T <- S4T + Tickets[i]
    S4R <- S4R + (Tickets[i] * PricePerTicket[i])
  }
}

##Calculate Parking Metrics
BP = 0
BPP = 0
BPR = 0

PG = 0
PGP = 0
PGR = 0

FF = 0
FFP = 0
FFR = 0

WL = 0
WLP = 0
WLR = 0

F4P = 0
F4PP = 0
F4PR = 0

NOP = 0

for (i in 1:nrow(STH)) {
  if (ParkingLocation[i] == "Baseball Lot") { 
    BP <- BP + 1
    BPP <- BPP + ParkingPasses[i]
    BPR <- BPR + (ParkingPasses[i] * PricePerPass[i])
  }
  else if (ParkingLocation[i] == "Parking Garage") {
    PG <- PG + 1
    PGP <- PGP + ParkingPasses[i]
    PGR <- PGR + (ParkingPasses[i] * PricePerPass[i])
  }
  else if (ParkingLocation[i] == "Freshman Field") {
    FF <- FF + 1
    FFP <- FFP + ParkingPasses[i]
    FFR <- FFR + (ParkingPasses[i] * PricePerPass[i])
  }
  else if (ParkingLocation[i] == "West Lot") {
    WL <- WL + 1
    WLP <- WLP + ParkingPasses[i]
    WLR <- WLR + (ParkingPasses[i] * PricePerPass[i])
  }
  else if (ParkingLocation[i] == "Fitton 4") {
    F4P <- F4P + 1
    F4PP <- F4PP + ParkingPasses[i]
    F4PR <- F4PR + (ParkingPasses[i] * PricePerPass[i])
  }
  else {
    NOP <- NOP + 1
  }
}
```

**Part I: 2022 (Thus Far)**

According to a report from Audience View, the Total Number of Season Ticket Accounts, Season Tickets Sold, and Season Ticket Revenue for this upcoming season is as follows:

|       | Total Season Ticket Accounts | Total Season Tickets Sold | Total Season Ticket Revenue |
|:-----:|:----------------------------:|:-------------------------:|:---------------------------:|
| 2022* |              325             |            803            |            $74,400            |

Breaking this down into Renewed Ticket metrics and New Ticket Metrics, we get the following:

|       | Renewed Accounts | Renewed Tickets | Renewed Revenue |
|:-----:|:----------------:|:---------------:|:---------------:|
| 2022* |        268       |       662       |      $60,980      |

|       | New Accounts | New Tickets | New Revenue |
|:-----:|:------------:|:-----------:|:-----------:|
| 2022* |      58      |     143     |    $13,640    |

**Note: The 2022 Season Ticket Program is still available for Purchase. These values are subject to change.**

From the same report, the Total Number of Parking Accounts, Parking Passes, and Parking Revenue is as follows:

|       | Total Parking Accounts | Total Parking Passes | Total Parking Revenue |
|:-----:|:----------------------:|:--------------------:|:---------------------:|
| 2022* |           252          |          263         |         $25,995         |

Breaking this down into Individual Parking Lot Metrics, we get the following:

|                | Accounts | Parking Passes | Revenue |
|:--------------:|:--------:|:--------------:|:-------:|
|  Baseball Lot*  |    138   |       143      |  $21,450  |
| Freshman Field* |    64    |       68       |   $2,380  |
|    West Lot*    |    14    |       14       |   $490   |
| Parking Garage* |    37    |       38       |   $1,710  |

**Note: The 2022 Season Ticket Program is still available for Purchase. These values are subject to change.**

On the surface, this all looks great, these two programs combined have earned over $100,000. But we cannot just conclude this based on these numbers alone. To get a better understanding of these numbers, we can compare these numbers to past seasons. 

\pagebreak

**Part II: How does this compare to past years?**

```{r, include = F}
##Read in Data For Graphs
STRR <- read.csv("2016_2021FBSeasonTicketRevenueReport.csv")
attach(STRR)

PRR <- read.csv("2016_2021FBParkingRevenueReport.csv")
attach(PRR)
```

```{r, include = F}
##Recalculate Renewal Rates
AccountRenewalRate <- RenewalRate
for (i in 1:5) {
  AccountRenewalRate[i] <- RenewedSeasonTicketAccounts[i] / TotalSeasonTicketAccounts[i+1]
  AccountRenewalRate[i] <- AccountRenewalRate[i] * 100
}
AccountRenewalRate <- round(AccountRenewalRate, digits = 2)

TicketRenewalRate <- RenewalRate
for (i in 1:4) {
  TicketRenewalRate[i] <- RenewedSeasonTickets[i] / TotalSeasonTickets[i+1]
  TicketRenewalRate[i] <- TicketRenewalRate[i] * 100
}
TicketRenewalRate <- round(TicketRenewalRate, digits = 2)
```

We will start by looking at season ticket metrics. Season plots for Total Season Ticket Accounts, Total Season Tickets Sold, and Total Season Ticket Revenue are provided below:

```{r, out.width = "50%", out.height = "50%"}
##Season Ticket Metrics

##Season Ticket Accounts per Season
plot(STRR$Year, TotalSeasonTicketAccounts, type = "l", lwd = 3, col = "red", 
     main = "Total Season Ticket Accounts each Season", 
     xlab = "Season", ylab = "Accounts")

##Season Tickets per Season
plot(STRR$Year, TotalSeasonTickets, type = "l", lwd = 3, col = "red", 
     main = "Total Season Tickets Sold each Season", 
     xlab = "Season", ylab = "Tickets Sold")

##Season Ticket Revenue per Season
plot(STRR$Year, TotalSeasonTicketRevenue, type = "l", lwd = 3, col = "red", 
     main = "Total Season Ticket Revenue each Season", 
     xlab = "Season", ylab = "Revenue ($)")
```

**Note: The 2022 Season Ticket Program has not closed. Therefore, these numbers are subject to change.**

Although there are drops in the overall number of Season Ticket Accounts and Season Tickets purchased, the overall Revenue earned from said Season Ticket Sales has increased this past season. There is a simple explanation for why this is. The price for each type of season ticket has increased this past season, so even though we are selling fewer tickets, we are still hitting the revenue marks. However, this business model is not necessarily sustainable. With the recent success of the Football Team, the price increases are justified, but if the team starts to perform worse, ticket prices cannot remain this great. 

\pagebreak

Breaking this down into terms of Renewed Season Tickets, and New Season Tickets, we get the following tables:

|       | Accounts Renewed | Tickets Renewed | Ticket Revenue Renewed | Renewal Rate |
|:-----:|:----------------:|:---------------:|:----------------------:|:------------:|
| 2022* |        268       |       662       |         $60,980        |    72.63%    |
|  2021 |        188       |       456       |         $26,210        |    63.73%    |
|  2019 |        225       |       531       |         $28,235        |    63.74%    |
|  2018 |        239       |       453       |         $20,862        |    78.88%    |
|  2017 |        225       |       420       |       $19,383.35       |    80.07%    |
|  2016 |        206       |       381       |       $16,236.20       |    73.30%    |

|      | New Accounts | New Season Tickets | New Ticket Revenue |
|:----:|:------------:|:------------------:|:------------------:|
| 2022 |      56      |         133        |       $12,700      |
| 2021 |      181     |         444        |       $25,735      |
| 2019 |      70      |         164        |       $9,867       |
| 2018 |      114     |         248        |       $11,475      |
| 2017 |      78      |         149        |      $7,230.50     |
| 2016 |      75      |         166        |      $7,044.40     |

With these tables, we can see why there have been decreases in both the total number of Season Ticket Accounts and Season Tickets Sold this past season. The 2021 Season saw a record number of New Season Ticket Holders and hence, a record number of New Season Tickets Sold. Although we have seen a record number of Renewed Season Ticket Accounts and Renewed Season Tickets Sold for the 2022, the New Season Ticket Accounts and New Season Tickets Sold for this past year are record lows. The Overall gain in Renewed Metrics, does not make up for the overall losses in New Metrics. 

However, this is not necessarily a bad thing. Having high Renewed Metrics means that fan retention is not an issue, the issue is getting new fans in the door. It stands to reason that a sizable proportion of New Accounts are parents and/or relatives of incoming Freshman class, so reaching out to them is paramount to growing these metrics. 

Now, shifting our focus away from Renewed vs. New, and instead focusing on Ticket Type, we get the following table:

|                   | Accounts | Tickets | Revenue |
|:-----------------:|:--------:|:-------:|:-------:|
|  Reserved Cushion |    86    |   224   |  $24640 |
| Reserved Bleacher |    198   |   499   |  $44910 |
| General Admission |    41    |    78   |  $5070  |
|   Fitton 4 Pack   |    12    |    14   |  $1960  |

**Note: Fitton 4 Pack is treated as its own category**

Here, we see that the Reserved Seating options are the most popular, with Cushion accounting for just under 28%, and Bleacher accounting for just over 62% of total tickets sold, respectively. Since these categories are the most popular, it stand to reason that these two categories also account for similar shares of the total revenue generated through ticket sales this year (Cushion = 33% of Revenue, Bleacher = 60.2% of Revenue).

\pagebreak

Next, we will take a look at Renewal Rates. As explained in previous reports, Renewal Rate can be thought of in terms of both an Account Renewal Rate, and a Ticket Renewal Rate. Plots for both of these metrics by season are provided below:

```{r, out.width = "50%", out.height = "50%"}
##Renewal Rate Metrics

##Account Renewal Rate per Season
plot(STRR$Year, AccountRenewalRate, type = "l", lwd = 3, col = "red", 
     main = "Account Renewal Rate each Season", 
     xlab = "Season", ylab = "Renewal Rate (%)")

##Ticket Renewal Rate per Season
plot(STRR$Year, TicketRenewalRate, type = "l", lwd = 3, col = "red", 
     main = "Ticket Renewal Rate each Season", 
     xlab = "Season", ylab = "Renewal Rate (%)")
```

**Note: The 2022 Season Ticket Program has not closed. Therefore, these numbers are subject to change.**

The non-issue of fan retention can be clearly seen from these two graphs. By definition, Renewal Rate is a metric to measure fan retention, by asking the question: *How many fans are returning to the program?* For the 2022 Season, we see that we have recovered from the renewal rate lows of the past season. we have observed significant increases in both the Account Renewal Rate, and Ticket Renewal Rate, with about a 10% increase in Account Renewal Rate and a 12% increase in Ticket Renewal Rate for the 2022 Season. 

\pagebreak

Finally, a look at Parking Metrics. Plots of Total Parking Paid Parking Accounts, Total Paid Parking Passes, and Total Parking Revenue are provided below:

```{r, out.width = "50%", out.height = "50%"}
##Parking Metrics

##Total Parking Accounts per Season
plot(PRR$Year, TotalPaidParkingAccounts, type = "l", lwd = 3, col = "red", 
     main = "Total Parking Accounts each Season", 
     xlab = "Season", ylab = "Accounts")

##Total Parking Passes per Season
plot(PRR$Year, TotalPaidParkingPasses, type = "l", lwd = 3, col = "red", 
     main = "Total Parking Passes each Season", 
     xlab = "Season", ylab = "Passes Sold")

##Total Parking Revenue per Season
plot(PRR$Year, TotalParkingRevenue, type = "l", lwd = 3, col = "red", 
     main = "Total Parking Revenue each Season", 
     xlab = "Season", ylab = "Revenue ($)")
```

**Note: The 2022 Season Ticket Program has not closed. Therefore, these numbers are subject to change.**

Similar to our graphs of Total Season Ticket Accounts, and Total Season Tickets Sold, the overall number of Parking Accounts and Parking Passes Sold have decreased this season. However, the overall revenue earned from said Parking Passes Sold this season has also decreased, unlike that for the Revenue earned through Season Ticket Sales. However, comparatively, the decrease in the Revenue earned from Parking Passes is not as significant as the decreases in the number of Total Parking Accounts and Total Parking Passes. 

\pagebreak

Now to break these graphs down in terms of the Accounts, Tickets, and Revenue, for each Individual parking lot. We will start by looking at the account share of each parking lot:

|      | Baseball Lot | Freshman Field | West Lot | Parking Garage |
|:----:|:------------:|:--------------:|:--------:|:--------------:|
| 2022 |      138     |       64       |    14    |       37       |
| 2021 |      158     |       65       |    23    |       124      |
| 2019 |      156     |       47       |    29    |       38       |
| 2018 |      150     |       52       |    19    |       38       |
| 2017 |      166     |       24       |     0    |       27       |
| 2016 |      168     |       15       |     0    |       20       |

Next is the parking pass share:

|      | Baseball Lot | Freshman Field | West Lot | Parking Garage |
|:----:|:------------:|:--------------:|:--------:|:--------------:|
| 2022 |      144     |       68       |    14    |       38       |
| 2021 |      174     |       85       |    34    |       136      |
| 2019 |      169     |       47       |    29    |       38       |
| 2018 |      166     |       53       |    21    |       39       |
| 2017 |      184     |       25       |     0    |       29       |
| 2016 |      190     |       16       |     0    |       22       |

And finally, the revenue earned from each parking lot:

|      | Baseball Lot | Freshman Field | West Lot | Parking Garage |
|:----:|:------------:|:--------------:|:--------:|:--------------:|
| 2022 |     $21450    |      $2380      |    $490   |      $1710      |
| 2021 |     $17400    |      $2975      |   $1190   |      $5440      |
| 2019 |     $8450     |      $1175      |   $1015   |       $950      |
| 2018 |     $8300     |      $1325      |    $735   |       $975      |
| 2017 |     $5520     |       $625      |     $0    |       $725      |
| 2016 |     $4750     |       $400      |     $0    |       $550      |

Here, we see that the majority of the decreases in Parking Accounts, Passes, and Revenue earned from said Passes can be explained by the significant decrease in the number of Parking Garage Accounts, Passes, and Revenue from the Garage. 

\pagebreak

Finally, the big picture: Total Revenue. A plot of the Total Revenue generated through Season Ticket Sales and Parking Pass Sales is provided below:

```{r}
##Total Revenue per Season
plot(STRR$Year, TotalRevenue, type = "l", lwd = 3, col = "red", 
     main = "Total Revenue each Season", 
     xlab = "Season", ylab = "Revenue ($)")
```

Overall, the amount of revenue generated from the Football Season Ticket and Football Parking Programs continues to increase each season, with the 2022 season being no exception. This upcoming season marks an important milestone with the program though, with it generating over 100 thousand dollars through Season Ticket and Parking Pass sales alone. 

\pagebreak

**Section II: Season Ticket Holder Trends**

```{r, inlcude = F}
##Remove Spring Football Season Ticket Orders from Data Set
##For Later Comparison
STH_SF <- STH[PaymentCreateDate != "4/9/2022", ]
```

Here are some breakdown plots and calculations for sale trends. First, we will group our orders by month. The result is displayed below: 

```{r}
##Barplot of Orders by Month
counts <- table(OrderMonth)
cols <- rainbow(length(counts))
barplot(counts, main = "Season Ticket Orders by Month", 
        xlab = "Month", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = cols)
box()
legend("topright", fill = cols, cex = 1, 
       legend = levels(factor(OrderMonth)))
```

|          |  April |   May  |  June |  July | August* |
|:--------:|:------:|:------:|:-----:|:-----:|:------:|
| # Orders |   204  |   95   |   16  |   23  |    0   |
| % Orders | 60.36% | 28.11% | 4.73% | 6.80% |  0.00% |

**Note: Renewals went live 4/9/2022**

**Updated: as of 8/1/2022**

Here, we see that the majority of the Football Season Ticket Orders for this season were placed within the first 21 days of them being available for purchase. A whopping 60% of orders were placed during this period. For the 2-month benchmark over 88% of orders were placed. The remaining months only make up just over 11% of all orders placed. This means that we should be targeting the first 2 months after the launch of Football Season Tickets to capture the most customers. In terms of renewals, it is safe to say that if they do not renew within the first 2 months, it is unlikely that they will renew before the start of the season. 

\pagebreak

Next, we have Orders grouped by the Day of the Week that they were placed. 

```{r, fig.align = "center", out.width = "65%", out.height = "65%"}
##Barplot of Orders by Day of the Week
counts <- table(STH$PaymentDoW)
barplot(counts, main = "Season Ticket Orders by Day of Week", 
        xlab = "Day of Week", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = rainbow(length(counts)))
box()
legend("topright", fill = rainbow(length(counts)), cex = .5, 
       legend = levels(factor(STH$PaymentDoW)))
```

| Sunday | Monday | Tuesday | Wednesday | Thursday | Friday | Saturday |   BD%  |
|:------:|:------:|:-------:|:---------:|:--------:|:------:|:--------:|:------:|
|   17   |   87   |    64   |     42    |    57    |   41   |    30    | 86.09% |

Since, Renewals opened the same day as a Saturday Spring Football Game, the orders placed on this day will be removed from the sample pool to generate clearer results. After doing this, we get the following: 

```{r, fig.align = "center", out.width = "65%", out.height = "65%"}
##Barplot of Orders by Day of the Week minus Spring Football
counts <- table(STH_SF$PaymentDoW)
barplot(counts, main = "Season Ticket Orders by Day of Week (minus Spring 
        Football)", 
        xlab = "Day of Week", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = rainbow(length(counts)))
box()
legend("topright", fill = rainbow(length(counts)), cex = .5, 
       legend = levels(factor(STH$PaymentDoW)))
```

| Sunday | Monday | Tuesday | Wednesday | Thursday | Friday | Saturday |   BD%  |
|:------:|:------:|:-------:|:---------:|:--------:|:------:|:--------:|:------:|
|   17   |   87   |    64   |     42    |    57    |   41   |     5    | 92.97% |

**Note: BD% is the percentage of orders made during a normal business week. (M-F)**

\pagebreak

```{r}
##Barplot of Orders by Time of Day
counts <- table(PaymentHour)
cols <- rainbow(length(counts))
barplot(counts, main = "Season Ticket Orders by Time of Day", 
        xlab = "Time of Day", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = cols)
box()
legend("topright", fill = cols, cex = .40, 
       legend = levels(factor(PaymentHour)))
```

|  **0:00** |  **1:00** |  **2:00** |  **3:00** |  **4:00** |  **5:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     0     |     1     |     0     |     1     |     0     |     0     |

|  **6:00** |  **7:00** |  **8:00** |  **9:00** | **10:00** | **11:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     3     |     4     |     9     |     9     |     56    |     51    |

| **12:00** | **13:00** | **14:00** | **15:00** | **16:00** | **17:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     44    |     39    |     32    |     39    |     17    |     5     |

| **18:00** | **19:00** | **20:00** | **21:00** | **22:00** | **23:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     4     |     6     |     5     |     6     |     6     |     1     |

For all 2022 Football Season Ticket Orders, almost 85% were placed during the course of a normal business day. Of these 85% of business day orders, 40.42% were placed in the morning, while 59.58% were placed during the afternoon, with the greatest percentage of orders during any consecutive 3-hour period coming from 10:00-1:00.

Also, for all 2022 Football Season Ticket Orders, over 73.1% were during the regular business day and week. 

**Note: A normal business day is defined as the hours 9:00-17:00**

\pagebreak

```{r, include = F}
##Create Ordered Factor for Payment Hour for STH_SF
PaymentHour <- STH_SF$PaymentTime
##Deletes Last 2 Characters from String
PaymentHour <- substr(PaymentHour, 1, nchar(PaymentHour)-2) 
##Appends "00 on to the End of the String
PaymentHour <- paste(PaymentHour, "00", collapse = NULL)
##Removes the Space in the Middle of the String
PaymentHour <- gsub(" ", '', PaymentHour)

##Set Payment Hour as an Ordered Factor
PaymentHour <- as.factor(PaymentHour)
PaymentHour <- ordered(PaymentHour, levels = c("0:00", "1:00", "2:00", "3:00",
                                               "4:00", "5:00", "6:00", "7:00", 
                                               "8:00", "9:00", "10:00", "11:00",
                                               "12:00", "13:00", "14:00", 
                                               "15:00", "16:00", "17:00", 
                                               "18:00", "19:00", "20:00", 
                                               "21:00", "22:00", "23:00"))
```

```{r}
##Barplot of Orders by Time of Day (minus Spring Football)
counts <- table(PaymentHour)
cols <- rainbow(length(counts))
barplot(counts, main = "Season Ticket Orders by Time of Day (minus Spring 
        Football)", 
        xlab = "Time of Day", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = cols)
box()
legend("topright", fill = cols, cex = .40, 
       legend = levels(factor(PaymentHour)))
```

|  **0:00** |  **1:00** |  **2:00** |  **3:00** |  **4:00** |  **5:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     0     |     1     |     0     |     1     |     0     |     0     |

|  **6:00** |  **7:00** |  **8:00** |  **9:00** | **10:00** | **11:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     3     |     4     |     7     |     9     |     54    |     47    |

| **12:00** | **13:00** | **14:00** | **15:00** | **16:00** | **17:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     41    |     35    |     31    |     39    |     13    |     4     |

| **18:00** | **19:00** | **20:00** | **21:00** | **22:00** | **23:00** |
|:---------:|:---------:|:---------:|:---------:|:---------:|:---------:|
|     3     |     4     |     5     |     5     |     6     |     1     |

Not including Spring Football, almost 86% of all Football Season Ticket Orders were placed during the course of a normal business day. Of these 86% of business day orders, 40.89% were placed in the morning, while 59.11% were placed during the afternoon, with the greatest percentage of orders during any consecutive 3-hour period coming from 10:00-1:00.

Not including Spring Football, over 79.9% of orders were placed during the regular business week and day. 

**Note: A normal business day is defined as the hours 9:00-17:00**

\pagebreak

```{r}
##Orders by Delivery Method
counts <- table(STH$DeliveryMethod)
cols <- rainbow(length(counts))
barplot(counts, main = "Season Ticket Orders by Delivery Method", 
        xlab = "Delivery Method", ylab = "Frequency", 
        ylim = c(0, max(counts) * 1.2), 
        col = cols)
box()
legend("topright", fill = cols, cex = .75, 
       legend = levels(factor(STH$DeliveryMethod)))
```

| Mobile Delivery | Print at Home | Mail | Subscription | Email |
|:---------------:|:-------------:|:----:|:------------:|-------|
|       197       |      109      |  15  |      15      | 2     |

Here, we see that the Mobile Delivery and Print at Home options are the most popular methods for Ticket Delivery. This makes sense nowadays since virtually everyone has access to a personal smartphone on their person at all times and/or a personal printer. These two categories account for 58.28% and 32.35% of all orders respectively, combining for over 90% of all orders. If these trends continue, there may be an argument for removing the other options for ticket delivery. 

\pagebreak